R for Clinical Study Reports and Submission

### 2021-08-29 index.Rmd
add efficacy ananylsis example
update manifest file

--- 
title: "R for Clinical Study Reports and Submission"
author: ["Yilong Zhang"]
knit: "bookdown::render_book"
description: >
  This book will teach you how to prepare tables, listings and figures for clinical study report and submit to regulatory agency, 
  the essential part of clinical trial development.

@@

```{r, include = FALSE}
library(bslib)
library(xml2)
library(downlit)
library(haven) 
library(dplyr) 
library(tidyr) 
library(r2rtf) 
```

@@

>>>>

--- 
title: "R for Clinical Study Reports and Submission"
author: ["Yilong Zhang", "Nan Xiao", "Keaven Anderson"]
knit: "bookdown::render_book"
description: >
  This book will teach you how to prepare tables, listings and figures for clinical study report and submit to regulatory agency, 
  the essential part of clinical trial development.

@@

```{r, include = FALSE}
library(bslib)
library(xml2)
library(downlit)
library(haven) 
library(dplyr) 
library(tidyr) 
library(r2rtf) 
library(knitr)
library(kableExtra)
```

@@

## List of Authors and Contributors

```{r, echo = FALSE}
contributors <- c(person("Yilong", "Zhang", email = "yilong.zhang@merck.com", role = "aut"), 
                  person("Nan", "Xiao", role = "aut"), 
                  person("Keaven", "Anderson", role = "aut"),
                  person("Yujie", "Zhao", role = "ctr"))
```

The document is maintained by a community. 
While reading the document, you can be a contributor as well. 
The quality of this document relies on you.

- Author: contribute majority content of at least one chapter. 
- Contributor: [contribute at least one commit to the source code](https://stash.merck.com/projects/BARDS/repos/r4csr/browse)

```{r}
data.frame(contributors = as.character(contributors)) %>%   
  kable(format = "html") %>%
  kable_styling()
```
